Utilizing widespread market comparison studies of eight contemporary aircraft closely fitting the RFP \cite{RFP} requirement range and capacity from different manufacturers, eras, and continents, the team was able to formulate an initial design fulfilling or exceeding the requirements for a 400 passenger, short to medium haul aircraft. Since then, key decisions have been made to utilize newfound technological advantages in composites and high-lift devices in order to improve the characteristics of the aircraft of this size for short haul (hundreds of NM) flights.  The steps towards iteratively sizing and measuring the performance of this aircraft have been made, as has a foundation for strong justification of team decisions regarding the final detailed design of the aircraft presented in this report.  Additionally, significant strides have be taken to define the aircraft's hydraulic, electrical, flight control, emergency, and environmental control systems, including adaptation of a state of the art avionics suite fulfilling and exceeding the autopilot requirements set forth by the AIAA RFP \cite{RFP}.

A considerable amount of care has been taken in regards to further optimization of the aircraft's subsystems, with special attention regarding the non-metallic wing and its structure in order to fulfil the team goal of designing the best possible high capacity, short range, low budget aircraft. Further definition in CAD and proving in FEA found an aircraft structure capable of safely handling gusts and extreme loads as defined by the FAA \cite{cfr}.  Additionally, a continuous verification of FAA CFR Part 25 \cite{cfr} requirements has been completed throughout all aspects of the aircraft and its design stages to ensure compliance across the aircraft.  As demonstrated in this report, Toucan's SAM Mk I has undergone a build up analysis of each major system outlined in this report, as well as an estimation of production timelines and both initial and service-life maintenance cost for varying block sizes.  Throughout this project, the team at Toucan has strode to develop a value-driven aircraft capable of exceeding client expectations while solving one of industry's toughest and omnipresent problems by applying a blend of new and proven technology and methodology to the design of the aircraft presented in this report.  

Time allowing, there are a number of aspects Team Toucan would enjoy further exploring in pursuit of delivering the best high capacity, short range aircraft.  Foremost, a comprehensive study on the worthiness of winglets on an economical plane designed more around saving weight than lessening drag would be influential to qualitatively deciding whether to equip SAM Mk I with them.  Additionally, an interactive 3D cockpit rendering could be value added for marketing purposes in the avionics section.  Furthermore, a lengthy discussion of and investigation into the benefits (weight savings) of a composite fuselage, quantified directly with respective cost increase in light of the manufacturing challenges surrounding it would possibly further justify (or disprove) Team Toucan's use of a hybrid design featuring a metallic fuselage instead of a fully composite build up across the entire aircraft.  Finally, detailed CFD and eventually model wing tunnel testing would go a long ways towards proving accurate aerodynamic data has been predicted, perhaps greatly opening up SAM Mk I's performance, as the empirical and vortex lattice-based methods used currently are known to be conservative.  



% \textcolor{red}{
% \begin{itemize}
%     \item Summarize your motivation, design objectives, proposed design, key performance metrics, and key differentiators. \checkmark (\textit{JC})
%     \item Discuss problems encountered (e.g. requirements not met) and recommendations for future study (if any). \checkmark (\textit{JC})
%     \item Summarize future work. \checkmark (\textit{JC})
% \end{itemize}}

%Finally, significant strides will be made defining the aircraft's hydraulic, electrical, and environmental control systems, including adaptation of a state of the art avionics suite fulfilling the autopilot requirements set forth by AIAA.